---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

library(TwoCircles)
```

[![Travis-CI Build Status](https://travis-ci.org/SMAC-Group/TwoCircles.svg?branch=master)](https://travis-ci.org/SMAC-Group/TwoCircles)
[![Project Status: Active](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Licence](https://img.shields.io/badge/licence-CC BY--NC--SA 4.0-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-6666ff.svg)](https://cran.r-project.org/)
[![CRAN](http://www.r-pkg.org/badges/version/TwoCircles)](https://cran.r-project.org/package=TwoCircles)
[![packageversion](https://img.shields.io/badge/Package%20version-0.1.0-orange.svg?style=flat-square)](commits/develop)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)

# `TwoCircles` Overview

This package implements various nonparametric methods for testing whether two circular samples come from the same population and allows to obtain its associated small-sample distribution. In particular, the following test are considered:

* `dixon`: for Dixon test,
* `rao`: for Rao test,
* `wilcox`: for Wilcoxon test,
* `vdw` for van der Waerden test.

The code below presents a simple example with the pigeons dataset of Schmidt-Koenig (1958).

```{r}
# Load dataset
data(pigeons)

# Dixon test (exact pvalue)
circular_test(pigeons$experimental, pigeons$control)

# Dixon test (approximated pvalue)
circular_test(pigeons$experimental, pigeons$control, type = "mc")
```

It is also possible to compare the exact distribution of the test statistic under $H_0$ to the one obtained by simulations. This can be done as follows:

```{r, fig.align='center', fig.width=8, fig.height=8, cache = TRUE}
par(mfrow = c(2,2))
plot(circular_test(pigeons$experimental, pigeons$control), cex.main = 0.7)
plot(circular_test(pigeons$experimental, pigeons$control, type = "mc", B = 10^2), cex.main = 0.7)
plot(circular_test(pigeons$experimental, pigeons$control, type = "mc", B = 10^4), cex.main = 0.7)
plot(circular_test(pigeons$experimental, pigeons$control, type = "mc", B = 10^6), cex.main = 0.7)
```

It is also possible to vizualize the (exact or approximated) distirbution of the test statistics under $H_0$.
This illustrated with Rao and Dixon tests on the same dataset.

```{r, fig.width=8, fig.height=4.5, cache = TRUE}
test_rao = circular_test(pigeons$control, pigeons$experimental, test = "rao")
test_rao
par(mfrow = c(1,2))
plot(test_rao, cex.main = 0.7)

test_wilcox = circular_test(pigeons$control, pigeons$experimental, test = "wilcox")
test_wilcox
plot(test_wilcox, cex.main = 0.7)
```

## Install Instructions

To install the `TwoCircles` package, there is currently one option: [GitHub](https://github.com/SMAC-Group/TwoCircles/).

```{r, eval = F}
# Install dependencies
install.packages(c("gRbase","circular"))

# Install the package from GitHub
devtools::install_github("SMAC-Group/TwoCircles")
```

## Monte-Carlo Approximation Illustration

The Monte-Carlo approach that is proposed here as an alternative 

```{r, cache=TRUE}
# Number of simulations
B = 500

# Initialisation
exact_pval = rep(NA, B)
mc_pval = matrix(NA, B, 3)

for (i in 1:B){
  # Simulate samples
  set.seed(i)
  X = runif(8, 0, 360)
  Y = runif(7, 0, 360)
  
  # Compute exact pvalue
  exact_results = circular_test(X, Y)
  exact_pval[i] = mean(exact_results$stat <= exact_results$cv$dist)
  
  # Compute MC pvalue
  mc_results = circular_test(X, Y, type = "mc", B = 1000)
  mc_pval[i,1] = (1 + sum(mc_results$stat <= mc_results$mc$dist))/(length(mc_results$mc$dist) + 1)
  mc_results = circular_test(X, Y, type = "mc", B = 10000)
  mc_pval[i,2] = (1 + sum(mc_results$stat <= mc_results$mc$dist))/(length(mc_results$mc$dist) + 1)
  mc_results = circular_test(X, Y, type = "mc", B = 100000)
  mc_pval[i,3] = (1 + sum(mc_results$stat <= mc_results$mc$dist))/(length(mc_results$mc$dist) + 1)
}
```

```{r, fig.align = 'center', fig.width = 10, fig.height = 3.25}
par(mfrow = c(1,3))
hist(100*(exact_pval-mc_pval[,1]), col = "lightgrey", probability = TRUE, xlab = "Exact p-value - MC p-value (%)", main = "B = 1,000", xlim = c(-0.5, 2))

hist(100*(exact_pval-mc_pval[,2]), col = "lightgrey", probability = TRUE, xlab = "Exact p-value - MC p-value (%)", main = "B = 10,000", xlim = c(-0.5, 2))

hist(100*(exact_pval-mc_pval[,3]), col = "lightgrey", probability = TRUE, xlab = "Exact p-value - MC p-value (%)", main = "B = 100,000", xlim = c(-0.5, 2))
```


