---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

library(circTest)
```

[![Travis-CI Build Status](https://travis-ci.org/SMAC-Group/circTest.svg?branch=master)](https://travis-ci.org/SMAC-Group/circTest)
[![Project Status: Active](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![Licence](https://img.shields.io/badge/licence-CC BY--NC--SA 4.0-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
[![minimal R version](https://img.shields.io/badge/R%3E%3D-3.4.0-6666ff.svg)](https://cran.r-project.org/)
[![CRAN](http://www.r-pkg.org/badges/version/simts)](https://cran.r-project.org/package=circTest)
[![packageversion](https://img.shields.io/badge/Package%20version-0.1.0-orange.svg?style=flat-square)](commits/develop)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-yellowgreen.svg)](/commits/master)

# `circTest` Overview

This package implements various nonparametric methods for testing whether two circular samples come from the same population and allows to obtain its associated small-sample distribution. In particular, the following test are considered:

* `dixon`: for Dixon test,
* `rao`: for Rao test,
* `ww`: for Wheeler-Watson,
* `wilcox`: for Wilcoxon test,
* `vdw` for van der Waerden test,
* `savage` for Savage test.

The code below presents a simple example with the pigeons dataset of Schmidt-Koenig (1958).

```{r}
# Load dataset
data(pigeons)

# Dixon test (exact pvalue)
circular_test(pigeons$experimental, pigeons$control)

# Dixon test (approximated pvalue)
circular_test( pigeons$experimental, pigeons$control, type = "mc")
```

It is also possible to compare the exact distribution of the test statistic under $H_0$ to the one obtained by simulations. This can be done as follows:

```{r, fig.align='center', fig.width=8, fig.height=8, cache = TRUE}
par(mfrow = c(2,2))
plot(circular_test(pigeons$experimental, pigeons$control), cex.main = 0.7)
plot(circular_test(pigeons$experimental, pigeons$control, type = "mc", B = 10^2), cex.main = 0.7)
plot(circular_test(pigeons$experimental, pigeons$control, type = "mc", B = 10^4), cex.main = 0.7)
plot(circular_test(pigeons$experimental, pigeons$control, type = "mc", B = 10^6), cex.main = 0.7)
```



It is also possible to vizualize the (exact or approximated) distirbution of the test statistics under $H_0$.
This illustrated with Rao and Wheeler-Watson tests on the same dataset.

```{r, fig.width=8, fig.height=4.5, cache = TRUE}
test_rao = circular_test(pigeons$control, pigeons$experimental, test = "rao")
test_rao
par(mfrow = c(1,2))
plot(test_rao, cex.main = 0.7)

test_ww = circular_test(pigeons$control, pigeons$experimental, test = "ww")
test_ww
plot(test_ww, cex.main = 0.7)
```

## Install Instructions

To install the `circTest` package, there is currently one option: [GitHub](https://github.com/SMAC-Group/circTest/).

```{r, eval = F}
# Install dependencies
install.packages(c("gRbase","circular"))

# Install the package from GitHub
devtools::install_github("SMAC-Group/circTest")
```


